Recruiting Chapter

### 2020-10-26 manuscript.Rmd
draft changes

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: pdf_document
csl: ./other/apa.csl
urlcolor: blue
---

```{r setup, include=FALSE}
library(knitr)

@@

@@

#pct_budget
#str(pct_budget)
#attributes(pct_budget)
kable(
  x = pct_budget, 
  col.names = c("Activity", "Private", "Public"),
  caption = "Percentage of budget allocated to marketing/recruiting activities by private non-profit 4yr and public 4yr institutions"
)
# 
```

>>>>

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2
csl: ./other/apa.csl
urlcolor: blue
---

```{r setup, include=FALSE}
library(knitr)
library(bookdown)

@@

<!--
As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la
 fig.cap="2-mode plot of visits by private colleges and universities", 
-->

```{r plot_g_2mode_privu, echo=FALSE, out.width = '100%'}
knitr::include_graphics("assets/figures/plot_g_2mode_privu.pdf")
```
As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la

@@

#pct_budget
#str(pct_budget)
#attributes(pct_budget)
kable(
  x = pct_budget, 
  col.names = c("Activity", "Private", "Public"),
  caption = "Percentage of budget allocated to marketing/recruiting activities by private non-profit 4yr and public 4yr institutions"
)
#  <div id="refs"></div>
```
